---
title: "KPMG"
author: "Thomas Nguyen"
date: "13/07/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```


```{r include = FALSE}
library(tidyverse)
library(readxl)
library(fpp3)
library(openxlsx)
library(naniar)
library(kableExtra)
```

```{r}
KPMG <- read_xlsx(here::here("data/KPMG_VI_New_raw_data_update_final.xlsx"), sheet = "CustomerDemographic", skip = 1) %>%
  mutate(DOB = convertToDate(DOB)) %>%
  select(-default)
```

```{r include = FALSE}
KPMG %>% miss_var_summary() %>% 
  kable(caption = "Missing values in the dataset",
        digits = 3) %>%
  kable_styling(bootstrap_options = 
                  c("striped", "hover")
                   ) 

```

```{r}
# Check for duplicate

a <- KPMG  %>% group_by(last_name, DOB) %>% filter (n()>1)
```

Dear Mr. A, manager of Analytics, Information & Modelling,
My name is Thomas from your team. 
After checking for the quality of the data from Sprocket Central Pty Ltd , I have found some issues:

1. Column "default" is unreadable.
2. Accuracy
There is 1 customer that were born in 1843, which is almost impossible. This must be an error (It should be marked with NA for future analysis)
3. Completeness
There are 4 columns that contain missing values: Job Title, Last Name, DOB and tenure
506 lines (or 12.650%) of Job title column are missing.
125 lines (or 3.125%) of last_name column is missing.
88 lines (or 2.2%) of DOB column is missing.
87 lines (or 2.175%) of tenure column is missing.

4. Consistency
The data seems to have good consistentcy

5. Currency
Value is up to date

6. Relevancy 
There is no meta data in the dataset


7. Validity

There are grammar errors anddifferent ways of recording data in gender columns: (Femal, F, M, U).
There are job title that share the same name (Eg. Developer I, Developer II), need to clarify this

8. Uniqueness
There is no duplicated data 
